\herschel\thanks{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-03-09 HOPS/photometry/ms.tex
updated for last clr clr figure
revised figures etc

\documentclass[manuscript]{aastex}

@@

%\documentclass[preprint2]{aastex}

@@

\slugcomment{To appear in Astrophysical Journal}

@@

\author{Babar Ali}
\affil{Space Sciences Institute, Boulder, CO}
\email{bali67@gmail.com}

\author{William J. Fischer\altaffilmark{a}}
\affil{NASA Goddard Space Flight Center, Greenbelt, MD, USA.}
\email{wjfischer@gmail.com}

\author{S. Thomas Megeath}
\affil{Ritter Astrophysical Observatory, Department of Physics and Astronomy, University of Toledo, Toledo, OH, USA}
\email{tommegeath@gmail.com}

\author{Elise Furlan}
\affil{Infrared Processing and Analysis Center, California Institute of Technology, 770 S. Wilson Ave., Pasadena, CA 91125, USA}
\email{furlan@ipac.caltech.edu}

\author{Amelia M. Stutz}
\affil{Max Planck Institute for Astronomy, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\email{stutz@mpia.de}

@@

\and

@@

\altaffiltext{a}{NASA Postdoctoral Program Fellow.}

@@

\begin{abstract}
We summarize and investigate observed far-infrared properties of 409 protostar candidates in the Orion~A and B clouds using data from the \herschel\ Space Observatory.  The observations were taken as part of the Open Time Key Program {\it HOPS} (\herschel\ Orion Protostar Survey, PI: S. T. Megeath).  We find spatial correlations in the observed flux ratios as a function of sub-regions in both the Orion~A and B clouds.  Using simulations, we rule out completeness bias as the sole cause for the observed correlations.  We offer differences in accretion properties and/or evolutionary status as, at least partially, responsible for the observed differences by sub-regions.  Both accretion properties and evolutionary status differences, in turn, may trace fundamental differences in the star-forming conditions in the respective environments.  \end{abstract}

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  All 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin\ (CAN SOMEONE WITH ACCESS TO RAW DATA CONFIRM THE LARGEST FOV?).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 409 sources in the final sample included here.  Note that \cite{furlan}\ also include one additional source from \cite{tobin}\ which was not available when the analysis for this work was completed.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 409 objects in this contribution.

@@

\subsection{The observed protostar sample}
\label{sec:protostars}
Table~\ref{tbl:obs} lists the final combined catalog (see below for Table details).  As noted above, in some groups, we coincidently observed additional protostars from the \citet{orion} \spitzer\ sample.  These sources happen to be located inside group fields-of-view.   Of note, \citet{pbrpaper} identified highly embedded additional protostars (the so-called PACS Bright Red Sources, PBRs).  Our final catalog includes all known protostars detected by \herschel\ in the Orion fields covered by our observations.
\par
We investigated HOPS images for additional protostar candidates that might have been missed by our earlier efforts.  \citet{pbrpaper} required a 160~\micron\ detection for improved reliability, and implemented additional thresholds to reduce contamination from extra-galactic sources.  As \citet{pbrpaper} showed, \spitzer\ observations did not identify, or in rare cases, detect all protostars in Orion.  Hence, the possibility remains that additional sources, perhaps with detections only in the 70~\micron\ filter, lurk within our data.  With detection in only one or two bands, however, it is increasingly difficult to properly characterize these sources and distinguish them from foreground or background objects.  It is likely necessary that additional protostar candidates here will require follow-up observations or analysis.  Nonetheless, these sources may impact statistical studies, and are tabulated.  The results of this effort will be described in a future contribution.
\par
The columns have the following meaning in Table~\ref{tbl:obs}.  Column~1 lists the unique three-digit HOPS identifier.  Columns~2~\&~3 list the J2000 equatorial coordinates as measured on the \herschel\ images and as reported by the DAOPHOT find algorithm \citep{psfphotometry}.  Column~4 lists the \herschel-assigned unique observation identifiers (OBSIDs, two per group as described in Section~\ref{sec:obs}).  Column~5 lists the 3-digit group number mentioned above.  Columns~6-11 list the \herschel\ photometry for the three Herschel/PACS bands.  Our photometry procedure is described in Section~\ref{sec:phot}.  The 70~\micron\ and 160~\micron\ flux densities are from our program.  The 100~\micron\ fluxes are added from the larger survey of the Orion region from the the Gould-Belt Key Program \citep{gb}.  The extraction of the 100\micron\ photometry is discussed in \cite{pbrpaper}.  Each photometry value is described by two columns: the first provides the photometry value itself, and the other, labelled flag, has the following meaning:   flag = 0 means the source is not observed. flag =1 means the photometry, as quoted, is the measured value,  flag = 2 means the value is an upper limit, and flag = 3 means that the measurement is from the PSF-photometry, not aperture photometry (see Section~\ref{sec:phot}).  Column~12 identifies the sub-region within the Orion~A and B clouds to which the HOPS source belongs.  The sub-region definitions are listed in Table~\ref{tbl:regions}.  Finally, Column~13 lists the UT observation day for the observations.  When a source was detected in more than one group (tile) we combined the measurements as a simple average.

\section{Data Processing \& Map-making}
\label{sec:dp}
\par
We start data processing at the level~1 stage from the Herschel Science Archive.  Level~1 contains calibrated timelines\footnote{Timelines are simply readouts from individual pixels ordered sequentially by time of observation.  Note that for our observations the PACS instrument was used with a fixed readout frequency of 10 Hz.} from individual PACS bolometers from which all instrumental effects have already been removed except for the low frequency noise component (the so-called 1/f noise\footnote{The so-called 1/f noise modifies the signal timelines by adding a drift component whose amplitude is a power-law function of its Fourier frequency.}).  Our processing mitigates the 1/f noise, combines the two independent orthogonal scan directions, and projects the timelines onto the final image of the field.  We will refer to these steps as 'map-making' hereafter.  The processing steps leading up to level~1 are described in \citet{pacs} and in the data processing guides for the Herschel Interactive Processing System, HIPE \cite{hipe}.  All data discussed here are based on the FM7 version of the PACS calibration \citep{pacscal} and processed with version 9 of the HIPE software.  Our final maps have spatial scales of 1.6\arcsec/pixel and 3.2\arcsec/pixel for the 70~\micron\ and 160~\micron\ PACS filters, respectively.  We used three different approaches for map-making that are described below.

@@

\subsection{MADmap branch}
\par
We compared our Scanamorphos reduced images with those produced by another map-making option available within HIPE: the MADmap branch based on a java implementation of the Maximum Anisotropy Dataset mapper (MADmap) software developed and described by \citet{madmap}.  As with Scanamorphos, MADmap images preserve fluxes on all spatial scales in the field-of-view.  At the time these data reductions were applied, the MADmap branch suffered from the so-called point-source-artifacts \citep{madarts}; Hence, the primary use of MADmap was in allowing us to check our Scanamorphos images for any spurious artifacts introduced by the map-making process.  We looked for structures that were present in one, but not both images from the two map-making approaches.  Such artifacts may result from the map-making process in fields such as Orion because the Fourier frequencies of extended, nebulous emission are similar in nature to  the low-frequency drift (the 1/f noise).  Thus, it becomes necessary to verify that the process by which 1/f noise is removed does not affect or alter flux from spatially extended sources.  The MADmap branch provided said quality control for our fields.

@@

\begin{deluxetable}{lccl}
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{The sub-region boundaries in the Orion A~\&~B clouds\label{tbl:regions}}
\tablehead{
\colhead{Name} &
\multicolumn{2}{c}{Declination Boundary (degrees)} &
\colhead{Number of protostars} \\
\colhead{}&
\colhead{Low} &
\colhead{High} &
\colhead{}
}
\startdata
LDN 1622 & 1.3 & 2.0833 & 11\\
NGC 2068 & -0.5 & 1.3 & 59 \\
NGC 2023/4 & -3.83 & -0.5 & 27\\
OMC 2/3 & -5.30 & -3.83 & 64\\
ONC-S & -6.10 & -5.30 & 54\\
LDN 1641-N & -6.90 & -6.10 & 47\\
LDN 1641-C & -7.60 & -6.90 & 62\\
LDN 1641-S & -9.0 & -7.60 85&
\enddata
\end{deluxetable}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=5in]{LFs.eps}
\caption{Flux distributions at 70~\micron\ (top, blue) and 160~\micron\ (bottom, red) for all sources in the HOPS sample.  The upper limits are not used to calculate the distribution.\label{fig:fd}}
\end{figure*}

\begin{figure*}[ht]
\centering
\includegraphics[height=7in]{LF70_byregion.eps}
\caption{The 70\micron\ flux distributions segregated by sub-region for Orion B (left column) and Orion A (right column).\label{fig:fd70regional}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=7in]{LF160_byregion.eps}
\caption{The 160\micron\ flux distributions segregated by subregion for Orion B (left column) and Orion A (right column).\label{fig:fd160regional}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{Figures/mdFlux_v_dec.eps}
\caption{Median flux as a function of declination for the 70~\micron\ FD (blue dots and curve) and the 160~\micron\ FD (red dots and curve).\label{fig:mdFlux_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{Figures/OrionA_clrclr.eps}
\caption{The observed distribution of colors in Orion~A segregated by sub-regions.  The sub-region is identified in the respective panel.  Solid red symbols show the colors for the sub-region.  Smaller black open symbols show the distribution for all sources in the combine Orion~A and Orion~B samples.\label{fig:clrclr1}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{Figures/OrionB_clrclr.png}
\caption{Same as Figure~\ref{fig:clrclr1} for Orion~B.\label{fig:clrclr2}}
\end{figure*}

@@

%7
\begin{figure*}[ht]
\centering
\plotone{Figures/clr1_vs_dec.png}
\caption{The mean (black circles) and median (red circles) value of \clra\ color as a function of declination.  The associated sub-region is labelled above the data points themselves.  The vertical bars show the respective standard deviation.  \label{fig:clr1_v_dec}}
\end{figure*}

@@

%8
\begin{figure*}[ht]
\centering
\plotone{Figures/clr2_vs_dec.png}
\caption{Same as Figure~\ref{fig:clr1_v_dec} for the \clrb\ color.  \label{fig:clr2_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{Figures/num_vs_dec.png}
\caption{Number of protostars as a function of sub-region in Orion.\label{fig:num_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plottwo{Figures/f70_v_clr1.png}{Figures/f70_v_clr2.png}
\caption{The observed 70~\micron\ flux as a function of the \clra\ (left) and \clrb\ (right) flux ratios.\label{fig:clrflux}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{Figures/clr_vs_flimit.png}
\caption{The observed mean color above the simulated completeness limit for LDN~1641.  Solid lines show the mean values for \clra\ (black) and \clrb\ (blue) with limiting flux.  The dashed lines show the mean color for the combined Orion ONC and OMC-2/3 region.  As discussed in text, we note a complete lack of correlation between the completeness limit and mean color for \clrb.  We note a steady increase in the mean \clra as a function of the completeness limit.  However, the average completeness limits require significant differences before the LDN 1641 sub0region can be explained as being similar to Orion OMC-2/3 and the ONC.\label{fig:clr_v_limit}}
\end{figure*}

@@

\bibitem[Fischer \etal\ (2016)]{will} Fischer, W., J., \etal, 2015, in prep.

>>>>

\documentclass[manuscript]{aastex61}

@@

%\documentclass[preprint2]{aastex}
%\documentclass[manuscript]{aastex61}

@@

\received{}
\revised{\today}
\accepted{}

\submitjournal{ApJ}

%\slugcomment{To appear in Astrophysical Journal}

@@

\correspondingauthor{Babar Ali}
\email{bali67@gmail.com}

\author{Babar Ali}
\affil{Space Sciences Institute, Boulder, CO}

\author{William J. Fischer}
\altaffiliation{NASA Postdoctoral Program Fellow.}
\affil{NASA Goddard Space Flight Center, Greenbelt, MD, USA.}

\author{S. Thomas Megeath}
\affil{Ritter Astrophysical Observatory, Department of Physics and Astronomy, University of Toledo, Toledo, OH, USA}

\author{Elise Furlan}
\affil{Infrared Processing and Analysis Center, California Institute of Technology, 770 S. Wilson Ave., Pasadena, CA 91125, USA}

\author{Amelia M. Stutz}
\affil{Max Planck Institute for Astronomy, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

@@

% \and

@@

@@

\begin{abstract}
We summarize and investigate observed far-infrared properties of 410 protostar candidates in the Orion~A and B clouds using data from the \herschel\ Space Observatory.  The observations were taken as part of the Open Time Key Program {\it HOPS} (\herschel\ Orion Protostar Survey, PI: S. T. Megeath).  We find spatial correlations in the observed flux ratios as a function of sub-regions in both the Orion~A and B clouds.  Using simulations, we rule out completeness bias as the sole cause for the observed correlations.  We offer differences in accretion properties and/or evolutionary status as, at least partially, responsible for the observed differences by sub-regions.  Both accretion properties and evolutionary status differences, in turn, may trace fundamental differences in the star-forming conditions in the respective environments.  \end{abstract}

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  All 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 409 sources in the final sample included here.  Note that \cite{furlan}\ also include one additional source from \cite{tobin}\ which was not available when the analysis for this work was completed.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 409 objects in this contribution.

@@

\subsection{The observed protostar sample}
\label{sec:protostars}
Table~\ref{tbl:obs} lists the final combined catalog (see below for Table details).  As noted above, in some groups, we coincidently observed additional protostars from the \citet{orion} \spitzer\ sample.  These sources happen to be located inside group fields-of-view.   Of note, \citet{pbrpaper} identified highly embedded additional protostars (the so-called PACS Bright Red Sources, PBRs).  Our final catalog includes all known protostars detected by \herschel\ in the Orion fields covered by our observations.
\par
We investigated HOPS images for additional protostar candidates that might have been missed by our earlier efforts.  \citet{pbrpaper} required a 160~\micron\ detection for improved reliability, and implemented additional thresholds to reduce contamination from extra-galactic sources.  As \citet{pbrpaper} showed, \spitzer\ observations did not identify, or in rare cases, detect all protostars in Orion.  Hence, the possibility remains that additional sources, perhaps with detections only in the 70~\micron\ filter, lurk within our data.  With detection in only one or two bands, however, it is increasingly difficult to properly characterize these sources and distinguish them from foreground or background objects.  It is likely necessary that additional protostar candidates here will require follow-up observations or analysis.  Nonetheless, these sources may impact statistical studies, and are tabulated.  The results of this effort will be described in a future contribution.
\par
The columns have the following meaning in Table~\ref{tbl:obs}.  Column~1 lists the unique three-digit HOPS identifier.  Columns~2~\&~3 list the J2000 equatorial coordinates as measured on the \herschel\ images and as reported by the DAOPHOT find algorithm \citep{psfphotometry}.  Column~4 lists the \herschel-assigned unique observation identifiers (OBSIDs, two per group as described in Section~\ref{sec:obs}).  Column~5 lists the 3-digit group number mentioned above.  Columns~6-13 list the \herschel\ photometry for the three Herschel/PACS bands.  Note these results were already reported by \cite{furlan} and are repeated here for convenience.  Our photometry procedure is described in Section~\ref{sec:phot}.  The 70~\micron\ and 160~\micron\ flux densities are from our program.  The 100~\micron\ fluxes are added from the larger survey of the Orion region from the the Gould-Belt Key Program \citep{gb}.  The extraction of the 100\micron\ photometry is discussed in \cite{pbrpaper}.  Each photometry value is described by three columns: the first provides the photometry value itself, the second, labelled flag, has the following meaning:   flag = 0 means the source is not observed. flag =1 means the photometry, as quoted, is the measured value,  flag = 2 means the value is an upper limit, and flag = 3 means that the measurement is from the PSF-photometry, not aperture photometry (see Section~\ref{sec:phot}).  The third column labelled 'Method' lists whether aperture or PSF photometry technique was used to obtain the measurement.  Column~14 identifies the sub-region within the Orion~A and B clouds to which the HOPS source belongs.  The sub-region definitions are listed in Table~\ref{tbl:regions}.  Finally, Column~15 lists the UT observation day for the observations.  When a source was detected in more than one group (tile) we combined the measurements as a simple average.

\section{Data Processing \& Map-making}
\label{sec:dp}
\par
We start data processing at the level~1 stage from the Herschel Science Archive.  Level~1 contains calibrated timelines\footnote{Timelines are simply readouts from individual pixels ordered sequentially by time of observation.  Note that for our observations the PACS instrument was used with a fixed readout frequency of 10 Hz.} from individual PACS bolometers from which all instrumental effects have already been removed except for the low frequency noise component (the so-called 1/f noise\footnote{The so-called 1/f noise modifies the signal timelines by adding a drift component whose amplitude is a power-law function of its Fourier frequency.}).  Our processing mitigates the 1/f noise, combines the two independent orthogonal scan directions, and projects the timelines onto the final image of the field.  We will refer to these steps as 'map-making' hereafter.  The processing steps leading up to level~1 are described in \citet{pacs} and in the data processing guides for the Herschel Interactive Processing System, HIPE \cite{hipe}.  All data discussed here are based on the FM7 version of the PACS calibration \citep{pacscal} and processed with version 9 of the HIPE software.  Our final maps have spatial scales of 1.6\arcsec/pixel and 3.2\arcsec/pixel for the 70~\micron\ and 160~\micron\ PACS filters, respectively.  We used two different approaches for map-making that are described below.

@@

@@

\begin{deluxetable}{lrrc}
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{The sub-region boundaries (in decimal degrees) for the Orion A~\&~B clouds\label{tbl:regions}}
\tablehead{
\colhead{Name} &
\multicolumn{2}{c}{Declination Boundary} &
\colhead{Number of protostars} \\
\colhead{}&
\colhead{Low} &
\colhead{High} &
\colhead{}
}
\startdata
LDN 1622     & 1.3     & 2.08   & 11\\
NGC 2068    & -0.5   & 1.3     & 59 \\
NGC 2023/4 & -3.83 & -0.5   & 27\\
OMC 2/3       & -5.3 & -3.83 & 64\\
ONC-S          & -6.1 & -5.3 & 54\\
LDN 1641-N & -6.9 & -6.1 & 47\\
LDN 1641-C & -7.6 & -6.9 & 62\\
LDN 1641-S & -9      & -7.6 & 85\\
\enddata
\end{deluxetable}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=5in]{figures/LFs.eps}
\caption{Flux distributions at 70~\micron\ (top, blue) and 160~\micron\ (bottom, red) for all sources in the HOPS sample.  The upper limits are not used to calculate the distribution.\label{fig:fd}}
\end{figure*}

\begin{figure*}[ht]
\centering
\includegraphics[height=7in]{figures/LF70_byregion.eps}
\caption{The 70\micron\ flux distributions segregated by sub-region for Orion B (left column) and Orion A (right column).\label{fig:fd70regional}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=7in]{figures/LF160_byregion.eps}
\caption{The 160\micron\ flux distributions segregated by subregion for Orion B (left column) and Orion A (right column).\label{fig:fd160regional}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/mdFlux_v_dec.eps}
\caption{Median flux as a function of declination for the 70~\micron\ FD (blue dots and curve) and the 160~\micron\ FD (red dots and curve).\label{fig:mdFlux_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/OrionA_clrclr.eps}
\caption{The observed distribution of colors in Orion~A segregated by sub-regions.  The sub-region is identified in the respective panel.  Solid red symbols show the colors for the sub-region.  Smaller black open symbols show the distribution for all sources in the combine Orion~A and Orion~B samples.\label{fig:clrclr1}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/OrionB_clrclr.eps}
\caption{Same as Figure~\ref{fig:clrclr1} for Orion~B.\label{fig:clrclr2}}
\end{figure*}

@@

%7
\begin{figure*}[ht]
\centering
\plotone{figures/clr1_vs_dec.eps}
\caption{The mean (black circles) and median (red circles) value of \clra\ color as a function of declination.  The associated sub-region is labelled above the data points themselves.  The vertical bars show the respective standard deviation.  \label{fig:clr1_v_dec}}
\end{figure*}

@@

%8
\begin{figure*}[ht]
\centering
\plotone{figures/clr2_vs_dec.eps}
\caption{Same as Figure~\ref{fig:clr1_v_dec} for the \clrb\ color.  \label{fig:clr2_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/num_vs_dec.eps}
\caption{Number of protostars as a function of sub-region in Orion.\label{fig:num_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/f70_v_clr2.eps}
\caption{The observed 70~\micron\ flux as a function of the \clra\ (left) and \clrb\ (right) flux ratios.\label{fig:clrflux}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/clr_vs_flimit.eps}
\caption{The observed mean color above the simulated completeness limit for LDN~1641.  Solid lines show the mean values for \clra\ (black) and \clrb\ (blue) with limiting flux.  The dashed lines show the mean color for the combined Orion ONC and OMC-2/3 region.  As discussed in text, we note a complete lack of correlation between the completeness limit and mean color for \clrb.  We note a steady increase in the mean \clra as a function of the completeness limit.  However, the average completeness limits require significant differences before the LDN 1641 sub0region can be explained as being similar to Orion OMC-2/3 and the ONC.\label{fig:clr_v_limit}}
\end{figure*}

@@

\bibitem[Fischer \etal\ (2016)]{will} Fischer, W., J., \etal, 2017 submitted
